module2_eco_pol_factors

### 2022-02-27 moduletwoanalysis.Rmd
improved perceived risk graph

codedmodule2 %>%
  summarize_at(vars(starts_with(c("RISKY"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
  #add row index so later spreading indexed correctly
  add_rownames()%>%
  #melt to long format
  gather(technology, value, -rowname) %>%
  # separate risky from variable suffix
  separate(technology, c("Risky", "var"), extra = "merge", fill = "left") %>%
  #separate mean from variable prefix
  separate(var, c("technology", "summary")) %>%
  # spread summary values back to wide form
  spread(summary,value) %>%
  #clean up
  select(-rowname, -Risky) %>%
  arrange(mean)
```
```{r}
#plotting perceived risk from different technologies

@@

module2%>%
  filter(!row_number() %in% c(1,2)) %>% 
  select(starts_with("RISKY"))%>%
  gather(Technology, Perceived_Risk, Risky_Hydro:Risky_INDLPG, factor_key = TRUE)%>%
  separate(Technology, c("Risky", "Technology"), extra = "merge", fill = "left")%>%
  select(-Risky) %>%
  group_by(Technology, Perceived_Risk) %>%
  summarise(n=n())%>%
ggplot(aes(fill= Perceived_Risk, y=n, x=Technology)) + 
  geom_bar(position="fill", stat="identity")+
  coord_flip()

# fix ugly visual. Rearrange from extremely risky to not at all risky. Red to green, rather not say/Don't know should be grey

@@

codedmodule2 %>%
  summarize_at(vars(starts_with(c("Ben"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
  #add row index so later spreading indexed correctly
  add_rownames()%>%
  #melt to long format
  gather(technology, value, -rowname) %>%
  # separate Ben from variable suffix
  separate(technology, c("Ben", "var"), extra = "merge", fill = "left") %>%
  #separate mean from variable prefix
  separate(var, c("technology", "summary")) %>%
  # spread summary values back to wide form
  spread(summary,value) %>%
  #clean up
  select(-rowname, -Ben) %>%
  arrange(mean)

@@

# fix ugly visual. Rearrange from extremely beneficial to not at all beneficial. Green to red, rather not say/Don't know should be grey. Also facet wrap by INDividually owned and centrally owned technology.

@@

>>>>

risksummary <- codedmodule2 %>%
  summarize_at(vars(starts_with(c("RISKY"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
  #add row index so later spreading indexed correctly
  add_rownames()%>%
  #melt to long format
  gather(technology, value, -rowname) %>%
  # separate risky from variable suffix
  separate(technology, c("Risky", "var"), extra = "merge", fill = "left") %>%
  #separate mean from variable prefix
  separate(var, c("technology", "summary")) %>%
  # spread summary values back to wide form
  spread(summary,value) %>%
  #clean up
  select(-rowname, -Risky) %>%
  arrange(mean)%>%
  setNames(paste0('perceivedrisk.', names(.)))%>%
  rename(technology = perceivedrisk.technology)

risksummary

```{r}
#plotting perceived risk from different technologies

@@

colorsequence<- c("#8C4646","#D9695F","#F2A679","#F2D091","#5D8C7B","#808080")
df_barplot<-module2%>%
  filter(!row_number() %in% c(1,2)) %>% 
  select(starts_with("RISKY"))%>%
  gather(Technology, Perceived_Risk, Risky_Hydro:Risky_INDLPG, factor_key = TRUE)%>%
  separate(Technology, c("Risky", "Technology"), extra = "merge", fill = "left")%>%
  select(-Risky) %>%
  group_by(Technology, Perceived_Risk) %>%
  summarise(n=n())

df_barplot %>% ggplot(aes(fill= fct_rev(factor(Perceived_Risk, levels=c("Extremely risky", "Very risky","Moderately risky","Slightly risky","Not at all risky","Rather not say/Don't know"))), y=n , x=Technology)) + 
  geom_bar(position="fill",stat="identity")+
  scale_fill_manual("legend", values = c("Extremely risky" = "#8C4646", "Very risky" = "#D9695F", "Moderately risky" = "#F2A679", "Slightly risky" = "#F2D091","Not at all risky" = "#5D8C7B", "Rather not say/Don't know" = "#808080"))+
  coord_flip()+
  theme_classic()

# fix ugly visual. Rearrange from extremely risky to not at all risky. Red to green, rather not say/Don't know should be grey. Also facet wrap by INDividually owned and centrally owned technology.

@@

benefitsummary <- codedmodule2 %>%
  summarize_at(vars(starts_with(c("Ben"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
  #add row index so later spreading indexed correctly
  add_rownames()%>%
  #melt to long format
  gather(technology, value, -rowname) %>%
  # separate Ben from variable suffix
  separate(technology, c("Ben", "var"), extra = "merge", fill = "left") %>%
  #separate mean from variable prefix
  separate(var, c("technology", "summary")) %>%
  # spread summary values back to wide form
  spread(summary,value) %>%
  #clean up
  select(-rowname, -Ben) %>%
  arrange(mean)%>%
  setNames(paste0('perceivedbenefit.', names(.))) %>%
  rename(technology = perceivedbenefit.technology)
benefitsummary

@@

# fix ugly visual. Rearrange from extremely beneficial to not at all beneficial. Green to red, rather not say/Don't know should be grey. Also facet wrap by INDividually owned and centrally owned technology. Also arrange descending from most beneficial to least beneficial.

@@

```{r}
full_join(risksummary,benefitsummary, by = NULL, copy = FALSE, keep = FALSE) %>%
  select(technology, perceivedrisk.mean, perceivedbenefit.mean) %>%
   gather(key = "level", value = "mean",
       perceivedrisk.mean, perceivedbenefit.mean) %>%
  ggplot(aes(x=technology, y= mean, fill = level))+
  geom_bar(stat="identity", position=position_dodge())+
  coord_flip()

# arrange descending and facet wrap by IND prefix

```{r}
full_join(risksummary,benefitsummary, by = NULL, copy = FALSE, keep = FALSE) %>%
  select(technology, perceivedrisk.median, perceivedbenefit.median) %>%
   gather(key = "level", value = "median",
       perceivedrisk.median, perceivedbenefit.median) %>%
  ggplot(aes(x=technology, y= median, fill = level))+
  geom_bar(stat="identity", position=position_dodge())+
  coord_flip()

# arrange descending and facet wrap by IND prefix
